term papaer 2

### 2024-02-13 outputs/paper/paper.qmd
paper

```{r}
#| label: fig-statements
#| fig-cap: "University degree"
#| echo: false
#| message: false
#| warning: false

p <- ggplot(data = election, aes(x = tse_code, y = edu_univ)) +
  geom_point(color = "blue") +  # Scatter plot points
  labs(x = "Number of registered voters", y = "University degree \n (fraction")
p + geom_smooth(method = "lm", color = "red")
```

@@

```{r}
#| label: tbl-hatemodel
#| tbl-cap: "Tabulated weights of linear regression models 1 through 6 using ordinary least squares. In parentheses are the standard errors. Asterisks denote ranges of p-values as described in the table footer."
#| echo: false
#| message: false
#| warning: false

@@

## Canadian Relevance: Case Study on Alberta's population ratios, dating markets and anti-refugee sentiments

>>>>

@@

```{r}
#| label: fig-model
#| fig-cap: "Tabulated weights of linear regression models 1 through 6 using ordinary least squares. In parentheses are the standard errors. Asterisks denote ranges of p-values as described in the table footer."
#| echo: false
#| message: false
#| warning: false

p <- ggplot(data = election, aes(x = inc_0_50_post, y = unempl_post)) +
  geom_point(color = "blue") +  # Scatter plot points
  labs(x = "Low income rate", y = "Unemployment rate")
p + geom_smooth(method = "lm", color = "red")
```

@@

## Canadian Relevance: Case Study on Alberta's

## population ratios, dating markets and anti-refugee sentiments
